Sequential rank agreement methods for comparison of ranked lists

### 2015-04-13 latex/paper.Rnw
Small text update

\title{Sequential rank agreement methods for comparison of ranked lists}
\author{}

@@

<<>>=
library(SuperRanker)
@

>>>>

\title{Sequential rank agreement methods for comparison of ranked lists}
\author{Claus Thorn Ekstrøm and Thomas Alexander Gerds and Kasper Brink-Jensen}

@@

<<fig=TRUE, echo=FALSE>>=
library(SuperRanker)
library(glmnet)
library(minerva)
library(changepoint)
library(randomForestSRC)

# Read data
library(multtest)
data(golub)

y <- golub.cl
x <- golub

producelists <- function(x, y) {
    index <- seq(1, nrow(golub))
                                        # d <- data.frame(y, x)

                                        # Marginale t-tests
    mt.p <- sapply(index, function(i) { t.test(x[i,] ~ y)$p.value } )
    list1 <- order(mt.p)

                                        # Marginale logreg-tests
    mlogreg.p <- sapply(index, function(i) { drop1(glm(y ~ x[i,], family=binomial), test="Chisq")[2,5] } )
    list2 <- order(mlogreg.p)

                                        # Elastic net
    X <- scale(t(x))
    enet <- glmnet(X, y, family="binomial", alpha=.8)
    nyres <- cv.glmnet(X, y, family="binomial", alpha=.8)
    coefficients <- coef(enet, s=nyres$lambda.1se)[-1]
    nonzeros <- sum(coefficients!=0)
    list3 <- order(abs(coefficients), decreasing=TRUE)

                                        # MIC
    MIC <- sapply(index, function(i) { mine(x[i,], y)$MIC})
    list4 <- order(MIC, decreasing=TRUE)

                                        # Random Forest
###    dd <- data.frame(y=factor(y), t(x))
                                        # dd <- data.frame(y=y, t(x))
###    f1 <- rfsrc(y ~ ., data=dd, ntree=100)
###    variables <- abs(f1$importance[,1])
###    num.undecided <- sum(variables==0)
###    list5 <- order(variables, decreasing=TRUE)
###    list5[(length(variables)-num.undecided):length(variables)] <- 0

    cbind(list1,list2,list3,list4)
}

inputmatrix <- producelists(x, y)
colnames(inputmatrix) <- c("T", "LogReg", "ElasticNet", "MIC", "RF")[1:ncol(inputmatrix)]

res <- sqrt(sra(inputmatrix))

plot(res[1:1000], lwd=3, col="red", type="l", ylim=c(0,1300), ylab="Sequential rank agreement")

## 
null <- sqrt(random_list_sra(inputmatrix, B=1, n=100))
matlines(null, col="gray", lty=1)
@

<<echo=FALSE, results=hide>>=
xxx <- as.data.frame(inputmatrix[1:10,])
xxx
@

<<label=tab1,echo=FALSE,results=tex>>=
library(xtable)
print(xtable(xxx))
#print(xtable(xxx, caption = "Top 10 list of results", label = "tab:one",
#digits = c(0, 0, 2, 0, 2, 3, 3)), table.placement = "tbp",
#caption.placement = "top")
@
